Flagging gravitational wave sources from radio jet morphology

### 2015-03-11 Paper/paper.tex
Add new plots to paper

>>>>

\begin{figure*}
\begin{center}
  \begin{tabular}{ccc}
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_90.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_80.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_40.pdf}
  \end{tabular}
\end{center}
\caption{Jet structure in the source frame. $\beta=0.9, 0.8, 0.4$ from left to right.}
\label{fig:srcframe}
\end{figure*}

\begin{figure*}
\begin{center}
  \begin{tabular}{ccc}
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_90_obs.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_80_obs.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_40_obs.pdf}
  \end{tabular}
\end{center}
\caption{Jet structure in the observer frame. $\beta=0.9, 0.8, 0.4$ from left to right.}
\label{fig:obsframe}
\end{figure*}

\begin{figure*}
\begin{center}
  \begin{tabular}{ccc}
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_90_ang.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_80_ang.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta_0_40_ang.pdf}
  \end{tabular}
\end{center}
\caption{Jet structure in angular coordinates. $\beta=0.9, 0.8, 0.4$ from left to right.}
\label{fig:ang}
\end{figure*}
